Adaptive evolution with aneuploidy and mutation

### 2022-06-22 ms/ms.tex
update affil

\author[1,*]{Ilia Kohanovski}
\author[2,*]{Martin Pontz}
\author[3]{Avihu H. Yona}
\author[1,2,$\dagger$]{Yoav Ram}

\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[3]{Institute of Biochemistry, Food Science and Nutrition,
Robert H. Smith Faculty of Agriculture, Food and Environment,
The Hebrew University of Jerusalem, Israel}
\affil[*]{These authors contributed equally to this work}
\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}

>>>>

\author[1,2,*]{Ilia Kohanovski}
\author[1,*]{Martin Pontz}
\author[3]{Avihu H. Yona}
\author[1,$\dagger$]{Yoav Ram}

\affil[1]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[2]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[3]{Institute of Biochemistry, Food Science and Nutrition,
Robert H. Smith Faculty of Agriculture, Food and Environment,
The Hebrew University of Jerusalem, Israel}
\affil[*]{These authors contributed equally to this work}
\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}
